Learning Geometric and Cycle-Consistent Representations with Graph Convolutional Networks

### 2019-03-19 latex/iccv2019/main.tex

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
% Include other packages here, before hyperref.
% \usepackage[outdir=./]{epstopdf}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{3510} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{1}
\begin{document}

%%%%%%%%% TITLE
% \title{All Graphs Lead to Rome: \\
% Cycle Consistent Multi-View Representations Using Graph CNNs}
\title{All Graphs Lead to Rome: Learning Geometric and Cycle-Consistent Representations with Graph Convolutional Networks}

\author{Stephen Phillips, Kostas Daniilidis \\
GRASP Laboratory, University of Pennsylvania\\
{\tt\small \{stephi, kostas\}@seas.upenn.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
% \and
% Second Author\\
% Institution2\\
% First line of institution2 address\\
% {\tt\small secondauthor@i2.org}
}

% When placing figures in \LaTeX, it's almost always best to use
% \verb+\includegraphics+, and to specify the  figure width as a multiple of
% the line width as in the example below
% {\small\begin{verbatim}
%    \usepackage[dvips]{graphicx} ...
%    \includegraphics[width=0.8\linewidth]
%                    {myfile.eps}
% \end{verbatim}
% }

@@

% Papers, excluding the references section,
% must be no longer than eight pages in length. The references section

%%%%%%%%% ABSTRACT
% We present a learning technique for refining multi-image feature matches in an unsupervised fashion.
\begin{abstract}
    Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Convolutional Network to learn an appropriate embedding function for aligning image features.
    We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to aquire.
    In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches that optimize cycle consistency directly.
    To the best of our knowledge, no other works have used learning for multi-image feature matching.
    Our experiments show that our method is competitive with other optimization based approaches.
\end{abstract}

@@

\subsubsection*{Acknowledgements}
Support by ARL DCIST CRA W911NF-17-2-0181, NSF-IIS-1703319, ARL RCTA W911NF-10-2-0016, ONR N00014-17-1-2093, and the Honda Research Institute is gratefully acknowledged.

{\small
\bibliographystyle{ieee}
\bibliography{mybib}
}

\newpage
\onecolumn

\section*{Appendix}

\subsection*{A. Relative Efficiency Against Optimization Based Methods}

In figure \ref{fig:iterplot} we show a more fine grained comparison of our algorithm to optimization based methods at different numbers of iterations.
We show the mean and standard devation of the errors of all methods, testing the optimization based methods at different iterations.

%------------------------------------------------------------------------
\begin{figure*}[ht]
\begin{center}
  \includegraphics[width=0.9\linewidth]{figures-IterationsPlot.pdf}
\end{center}
  \caption{
    This figure plots the average accuracy of the optimization methods by iteration compared to 12 iterations of our GCN based method.
    The bold center line shows the mean, the colored in region shows 1 standard devation of the errors.
    As we optimize for $L_1$ error, our method's $L_1$ loss is substantially better than its $L_2$ losses.
    The right most plot shows time, plotted on a log scale for clarity.
  }
\label{fig:iterplot}
\label{fig:onecol}
\end{figure*}

\subsection*{B. Effect of Group Normalization}
We observe that training with group normalization helps with training and generalization error, as shown in figure \ref{fig:groupnorm}.
As the Group Normalization operation is not easily parallelized across nodes in the graph, the use of Group Normalization is the main barrier to parallelization.
Thus we will need to find alternative more parallelizable methods to improve generalization error for future work.

%------------------------------------------------------------------------
\begin{figure*}[!hb]
\begin{center}
  \includegraphics[width=0.8\linewidth]{figures-GroupNormTest.pdf}
\end{center}
  \caption{
    This figure plots the training curves of the network with and without Group Normalization.
    Note that while the train/test curves are fairly similar with or without Group Normalization, distance to the ground truth is improved greatly with Group Normalization.
  }
\label{fig:groupnorm}
\label{fig:onecol}
\end{figure*}

>>>>

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcvfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{Learning Geometric and Cycle-Consistent Representations with Graph Convolutional Networks}

\author{Stephen Phillips, Kostas Daniilidis \\
GRASP Laboratory, University of Pennsylvania\\
{\tt\small \{stephi, kostas\}@seas.upenn.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
    Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Convolutional Network to learn an appropriate embedding function for aligning image features.
    We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to aquire.
    In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches that optimize cycle consistency directly.
    To the best of our knowledge, no other works have used learning for multi-image feature matching.
    Our experiments show that our method is competitive with other optimization based approaches.
\end{abstract}

@@

% \subsubsection*{Acknowledgements}
% Support by ARL DCIST CRA W911NF-17-2-0181, NSF-IIS-1703319, ARL RCTA W911NF-10-2-0016, ONR N00014-17-1-2093, and the Honda Research Institute is gratefully acknowledged.
% 
{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}
